\setcounter{page}{3}
\chapter*{Abstract}

The clustering problem is one of the fundamental problems in unsupervised machine learning, and arises in a wide scope of applications. The clustering problem is a nonconvex and nonsmooth optimization problem. 
We propose two clustering center-based algorithms, each tackles a different distance function. The KPALM algorithm solves the clustering problem with the squared Euclidean distance, whereas the $\varepsilon$-KPALM algorithm solves the clustering problem with the standard Euclidean distance. 
Both algorithms perform Alternating Minimization. For fixed centers each algorithm reassigns the data points, solving a minimization subproblem, whose objective is a linear function regularized with a proximal term. For fixed partition of the data points, both algorithms update the centers of the clusters. KPALM solves the subproblem via an exact minimization, whereas $\varepsilon$-KPALM solves approximated minimization subproblem performing a certain gradient step.
We prove the global convergence of these algorithms to a critical point via a new methodology which is based on the powerful Kurdyka-{\L}ojasiewicz property. 
As an illustration of the theoretical results, we present numerical tests which demonstrate the effectiveness of the proposed algorithms.


\addcontentsline{toc}{chapter}{Abstract}

\chapter*{Acknowledgements}

I would like to thank my advisor, Prof. Marc Teboulle, for introducing me to the interesting world of continuous optimization during my graduate studies. I am deeply grateful to Prof. Teboulle for motivating and encouraging me to research the clustering problem and for his helpful ideas how to tackle this interesting and important problem.

I would like to acknowledge my co-advisor, Prof. Shoham Sabach, for his insightful comments and constructive criticisms at different stages of my research and for his dedication and patience in helping me to complete this thesis.

None of this would have been possible without the support of my family, to whom this thesis is dedicated to. My family has been a constant source of love, concern, support and strength.

Finally, I appreciate the financial support from Tel-Aviv university which enabled me to focus on my research, and achieve this thesis.
\\
\\
\noindent February 2016\\
\noindent Sergey Voldman


\addcontentsline{toc}{chapter}{Acknowledgements}

\nobreak
