\documentclass[12pt,a4paper]{report}

\usepackage{latexsym,amssymb,amsmath}
\usepackage{mathdefs}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{enumerate}
\usepackage[T1]{fontenc}
%\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{rotating}
\usepackage{multirow}
%\usepackage{caption}

\usepackage{cleveref}
\usepackage{enumerate}
\usepackage{framed}
\usepackage{amsthm}
\usepackage{makeidx}
\usepackage{xfrac}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{epstopdf}
\usepackage{booktabs}
\usepackage{ltxtable} 


%%%%%% Size %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% START OF DEFINITIONS
%%%%%% Size %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\marginparwidth}{0in} \setlength{\marginparsep}{0in}
\setlength{\oddsidemargin}{0in} \setlength{\evensidemargin}{0in}
\setlength{\textwidth}{6.in} \setlength{\topmargin}{0in}
\setlength{\textheight}{9.in}

%********************** General Definitions ******************************

\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}{Definition}[section]
\newtheorem{example}{Example}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{remark}{Remark}[section]%
\newtheorem{lemma}{Lemma}[section]
\newtheorem{assumption}{Assumption}[section]
\newtheorem{corollary}{Corollary}[section]
\def\nr{\par \noindent}
% END OF DEFINITIONS
%******************* Counters etc ************************************* %
\renewcommand{\baselinestretch}{1.2}

%\renewcommand{\theequation}{\thesection.\arabic{equation}} % Equation numbering with subsections
\newcommand{\sect}[1]{\setcounter{equation}{0}\section{#1}} %
\def\theequation{\thesection.\arabic{equation}}


%\newcommand{\qed}{\hfill $\Box$ \nr \medskip} %End of proof
%\newcommand{\qed}{\hfill\BlackBox\\[2mm]} % End of proof.

% Different font in captions
\newcommand{\captionfonts}{\small}


\makeatletter  % Allow the use of @ in command names
\long\def\@makecaption#1#2{%
  \vskip\abovecaptionskip
  \sbox\@tempboxa{{\captionfonts #1: #2}}%
  \ifdim \wd\@tempboxa >\hsize
    {\captionfonts #1: #2\par}
  \else
    \hbox to\hsize{\hfil\box\@tempboxa\hfil}%
  \fi
  \vskip\belowcaptionskip}
\makeatother   % Cancel the effect of \makeatletter


\newcommand{\nn}{\mathbb{N}} %Nonnegative integers
\newcommand{\rr}{\mathbb{R}} %Real numbers
\newcommand{\norm}[1]{\left\Vert {#1} \right\Vert} %Norm
\def\abs#1{\left\lvert#1\right\rvert}

%*******************************************************

% etc
%

\begin{document}

%
%--------- Title
%
\include{title}
%
%--------- Start numbering preface in roman
%
\pagenumbering{roman}
%
%--------- Preface
%
\include{preface}
%
\tableofcontents
\newpage

\listoftables
\newpage

\listoffigures
\newpage

%
%--------- Start from Page 1
%
\pagenumbering{arabic}



\include{chapter1}

\include{chapter2}

\include{chapter3}

\include{chapter4}

\include{chapter5}

\newpage

%------------REFERRENCES------------------------------------------

\begin{thebibliography}{99}

\bibitem{AB2009} H. Attouch, J. Bolte. On the convergence of the proximal algorithm for nonsmooth functions involving analytic features. \emph{Math. Program.}, Vol. 116, pp. 5-16 (2009).


\bibitem{ABS2013}  H. Attouch, J. Bolte, B.F. Svaiter. Convergence of descent methods for semi-algebraic and tame problems: proximal algorithms, forward-backward splitting, and regularized Gauss-Seidel methods. \emph{Math. Program.}, Vol. 137, 91-129 (2013).


\bibitem{BS2015} A. Beck, S. Sabach. Weiszfeld's Method: Old and New Results. \emph{Journal of Optimization Theory and Applications}, Vol. 164, pp. 1-40 (2015).


\bibitem{BTC2008} A. Beck, M. Teboulle, Z. Chikishev. Iterative minimization schemes for solving the single source localization problem. \emph{SIAM J. Optim.}, Vol. 19, pp. 1397-1416 (2008).


\bibitem{BTY1991} A. Ben-Tal, M. Teboulle, W.H. Yang. A least-squares-based method for a class of nonsmooth minimization problems with applications in plasticity.  \emph{Applied Mathematics and Optimization}, Vol. 24, pp. 273-288 (1991).


\bibitem{B1981} J. Bezdek. \emph{Pattern Recognition with Fuzzy Objective Function Algorithms}. Plenum Press, New York (1981). 

\bibitem{BDL2006} J. Bolte, A. Daniilidis, A. Lewis. The {\L}ojasiewicz inequality for nonsmooth subanalytic functions with applications to subgradient dynamical systems. \emph{SIAM Journal of Optimization}, Vol 17, pp. 1205-1223 (2006).


\bibitem{BST2014} J. Bolte, S. Sabach, M. Teboulle. Proximal alternating linearized minimization for nonconvex and nonsmooth problems. \emph{Math. Program.}, Vol. 146, pp. 459-494 (2014).


\bibitem{CR1997} G. Chen, R. Rockafellar. Convergence rates in forward-backward splitting. \emph{SIAM Journal on Optimization}, Vol. 7, pp. 421-444 (1997).


\bibitem{DLR1977} A. P. Dempster, N. M. Laird, D. B. Rubin. Maximum Likelihood from Incomplete Data via the EM Algorithm. \emph{Journal of the Royal Statistical Society}, Vol. 39, pp. 1-38 (1977).


\bibitem{DHS2001} R. O. Duda, P. E. Hart, D. G. Stork. \emph{Pattern Classification}. John Wiley \& Sons, Inc., second edition (2001).


\bibitem{GJ1979} M.R. Garey, D.S. Johnson, \emph{Computers and Intractability: A Guide to the Theory of NP-Completeness}. W.H Freemen and Company, San Francisco, CA (1979).


\bibitem{JMF1999} A.K. Jain, M.N. Murty, P.J. Flynn. Data clustering: A review. \emph{ACM Computing Surveys}, Vol. 31 pp. 264-323 (1999).


\bibitem{LM1979} P. Lions, B. Mercier. Splitting algorithms for the sum of two nonlinear operators. \emph{SIAM Journal on Numerical Analysis} Vol. 16, pp. 964-979 (1979).


\bibitem{L1982} S.P. Lloyd. Least squares quantization in PCM. Bell Telephone Laboratories Paper, Murray Hill, NJ (1957). Also in, \emph{IEEE Transactions on Information Theory}, Vol. 28 pp. 127-135 (1982).


\bibitem{M1967} J. MacQueen. Some methods for classification and analysis of multivariate observations. In \emph{Proceedings of the fifth Berkeley Symposium on Math., Stat. and Probability}, pp. 281-296 (1967).


\bibitem{N2004} Y. Nesterov. \emph{Introductory Lectures on Convex Optimization: A Basic Course}. Springer Science \& Business Media, (2003).


\bibitem{M2005} M. Meila. Comparing Clusterings - An Axiomatic View. In \emph{ICML '05: Proceedings of the 22nd international conference on Machine Learning ACM}, New York, pp. 577-584 (2005).


\bibitem{SI1984} S.Z. Selim,  M.A. Ismail. K-Means-Type Algorithms. A Generalized Convergence Theorem and Characterization of Local Optimality. \emph{IEEE Transactions on Pattern Analysis and Machine Intelligence}, Vol. 6, pp. 81-87 (1984).


\bibitem{S1956} H. Steinhaus. Sur la division des corps materiels en parties. \emph{Bull. Acad. Polon. Sci.}, C1. III, Vol. IV, pp. 801-804 (1956). 


\bibitem{T2007} M. Teboulle. A Unified Continuous Optimization Framework for Center-Based Clustering Methods. \emph{The Journal of Machine Learning Research}, Vol. 8, pp. 65-102 (2007).


\bibitem{T1991} P. Tseng. Applications of a splitting algorithm to decomposition in convex programming and variational inequalities. \emph{SIAM Journal on Control and Optimization}, Vol. 29, pp. 119-138 (1991).


\bibitem{W1983}  C.F.J. Wu. On the Convergence Properties of the EM Algorithm. \emph{The Annals of Statistics}, Vol. 11 pp. 95-103 (1983).

\end{thebibliography}

\end{document}
